Stability and Performance of Coalitions of Prosumers Through Diversification in the Smart Grid

### 2016-02-17 Article.tex
intro modifs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Abstract
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Achieving a successful energetic transition through a smarter and greener electricity grid is a major goal for the 21st century. It is assumed that such smart grids will be characterized by bidirectional electricity flows coupled with the use of small renewable generators and a proper efficient information system. All these bricks might enable end users to take part in the grid stability by injecting power, or by shaping their consumption against financial compensation. In this paper, we propose an algorithm that forms coalitions of agents, called prosumers, that both produce and consume. It is designed to be used by aggregators that aim at selling the aggregated surplus of production of the prosumers they control. We rely on real weather data sampled across stations of a given territory in order to simulate realistic production and consumption patterns for each prosumer. This approach enables us to capture geographical correlations among the agents while preserving the diversity due to different behaviors. As aggregators are bound to the market operator by a contract, they seek to maximize their offer while minimizing their risk. The proposed graph based algorithm takes the underlying correlation structure of the agents into account and outputs coalitions with both high productivity and low variability. We show then that the resulting diversified coalitions are able to generate higher benefits on a constrained energy market, and are more resilient to random failures of the agents.
\end{abstract}

@@

In this paper, we consider agents in the distribution network that own both renewable distributed energy resources (DER) and loads. We will refer to these agents as prosumers \cite{Rathnayaka2012} in the future. If a prosumer produces more than he consumes, he might be willing to sell power. We thus assume the existence of an energy market where producers post a production capacity for an upcoming period, and buyers decide what bids to purchase. When the production is stochastic, as it can be with DER, this approach gets more complicated and risk should be quantified and taken into account. Rather than having a risk dependant price, we propose here a safer and simpler model. We assume the existence of a market operator who constrains the market entrance.

As single agents might not be productive or reliable enough, aggregators managing large portfolios of prosumers are more likely to enter such markets. A key point of this work is to merge the interests of the market operator and aggregators in a single utility function. While the aggregators intend to maximize their benefits with better contracts, the operator concerns are related to the quality and reliability of the market supply.

If a buyer purchases a contract, the corresponding aggregator has to inject the contracted amount of power at any time of the contract, exposing himself to financial penalties if he deviates. Since prosumers use renewables, we are concerned with the probability that the production falls below the contract value. In this case, storage or demand side managment might be solutions to avoid penalties, but this probability should still be maintained low.

@@

\begin{figure}
	\begin{center}
		\includegraphics[scale=.4]{Fig2}
		\caption{Process}
		\label{fig:process}
	\end{center}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Abstract
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In the context of the smart grid, we propose in this paper an algorithm that forms coalitions of agents, called prosumers, that both produce and consume. It is designed to be used by aggregators that aim at selling aggregated surplus of production of the prosumers they control. We rely on real weather data sampled across stations of a given territory in order to simulate realistic production and consumption patterns for each prosumer. This enables us to capture geographical correlations among the agents while preserving the diversity due to different behaviors. As aggregators are bound to the market operator by a contract, they seek to maximize their offer while minimizing their risk. The proposed graph based algorithm takes the underlying correlation structure of the agents into account and outputs coalitions with both high productivity and low variability. We show that the resulting diversified coalitions are able to generate higher benefits on a constrained energy market, and are more resilient to random failures of the agents.
\end{abstract}

@@

Achieving a successful energetic transition through a smarter and greener electricity grid is a major goal for the 21st century. It is assumed that such smart grids will be characterized by bidirectional electricity flows coupled with the use of small renewable generators and a proper efficient information system. All these bricks might enable end users to take part in the grid stability by injecting power, or by shaping their consumption against financial compensation.

In this paper, we consider agents in the distribution network that own both renewable distributed energy resources (DER) and loads. We will refer to these agents as prosumers \cite{Rathnayaka2012} in the future. If a prosumer produces more than he consumes, he might be willing to sell power. We thus assume the existence of an energy market where producers post a production capacity for an upcoming period, and buyers decide what bids to purchase. When the production is stochastic, as it can be with DER, this approach gets more complicated and risk should be quantified and taken into account. We thus assume the existence of a market operator who constrains the market entrance. As single agents might not be productive or reliable enough, aggregators managing large portfolios of prosumers are more likely to enter such markets. While there exists several models for fixing prices and organizing bids in such stochastic settings, the present work does not focus on transactions on the market. Instead, we study how aggregators can manage their portfolios as to maximize the production that they offer, given that such production is stochastic by nature. A key point of this work is then to merge the interests of the market operator and aggregators in a single utility function. While the aggregators intend to maximize their benefits with better contracts, the operator concerns are related to the quality and reliability of the market supply (more information about the scenario can be found in \cite{Europe} page 67-68). If a buyer purchases a contract, the corresponding aggregator has to inject the contracted amount of power at any time of the contract, exposing himself to financial penalties if he deviates. Since prosumers use renewables, we are concerned with the probability that the production falls below the contract value. In this case, storage or demand side managment might be solutions to avoid penalties, but this probability should still be maintained low.

@@

\begin{figure}
	\begin{center}
		\includegraphics[scale=.39]{Fig2}
		\caption{Process}
		\label{fig:process}
	\end{center}
\end{figure}
